---
title: 'Homework 4: Bags, Forests, Boosts, oh my'
author: "Your Name Goes Here"
date: "2/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, message = F, warning = F, include = F}
library(tidyverse)
library(broom)
library(glmnet)
library(caret)
library(ISLR)
library(janitor)
library(stringr)
library(rpart)
library(rpart.plot)
library(partykit)
library(randomForest)
library(MASS)
library(gbm)
theme_set(theme_bw())
```

## Problem 1

Problem 7 from Chapter 8 in the text. To be specific, please use a sequence of
`ntree` from 25 to 500 in steps of 25 and `mtry` from 3 to 9 for by 1. 

## Answer 1
```{r}
set.seed(1)
df <- tbl_df(Boston)
inTraining <- createDataPartition(df$medv, p = .75, list = F)
training <- df[inTraining,]
testing <- df[-inTraining,]
```

```{r}
set.seed(1982)
trees <- seq(25,500, by=25)
mtry1 <- seq(3,9, by=1)
rf_boston_cv <- train(medv ~ .,
                      data = training,
                      method = "rf",
                      ntree = 500,
                      importance=T,
                      tuneGrid = data.frame(mtry = mtry1))
rf_boston_cv
```

```{r}
ntrees <- seq(25,500, by=25)
mse_test <- rep(NA, length(ntrees))
mtry1 <- seq(3,9, by=1)

for (nti in 1:length(ntrees)) {
  nt = ntrees[nti]
  rf_boston_cv <- randomForest(medv ~ .,
                      data = training,
                      mtry = mtry1,
                      ntree = nt,
                      importance=T)
  mse <- predict(rf_boston_cv, newdata = testing)
  mse_test[nti] <- mean((testing$medv-mse)^2)
}

df_mse <- as.data.frame(mse_test)
df_mse$trees <- seq(25,500, by=25)

p <- ggplot(df_mse, aes(x=trees, y=mse_test))
p + geom_point() + geom_line()
```

## Problem 2

Problem 8 from Chapter 8 in the text. Set your seed with 9823 and split into 
train/test using 50\% of your data in each split. In addition to 
parts (a) - (e), do the following:

1. Fit a gradient-boosted tree to the training data and report the estimated 
test MSE. 
2. Fit a multiple regression model to the training data and report the 
estimated test MSE
3. Summarize your results. 

a.
```{r}
carseats <- Carseats
set.seed(9823)
inTraining <- createDataPartition(carseats$Sales, p = .5, list = F)
training <- carseats[inTraining,]
testing <- carseats[-inTraining,]
```

b.
```{r}
r_tree <- rpart(Sales~., data = training)
r_tree
prp(r_tree)
plot(as.party(r_tree))
```

```{r}
pred_test <- predict(r_tree, newdata = testing)
mean((testing$Sales-pred_test)^2)
```

The test MSE is 4.48

c.
```{r}
set.seed(9823)

```

